Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-04-09 doc/paper.Rmd
add a few notes

-   In Manaus, the canopy is as green or greener in the dry season compared to the wet season [@guanPhotosyntheticSeasonalityGlobal2015], so dry season drought may result in relatively large increases in light penetration to the understory.
    \

@@

```{=html}
<!-- -->
```
-   Ecological Consequences of these patterns: an eye towards a drier/wetter future

>>>>

-   In Manaus, the canopy is as green or greener in the dry season compared to the wet season [@guanPhotosyntheticSeasonalityGlobal2015], so dry season drought may result in relatively large increases in light penetration to the understory.

-   refs in @leitoldNinoDroughtIncreased2018 peak in tree mortality can happen up to 3 years after drought event in experimental studies.
    Observational studies show mortality happening in same year as 2007 and 2010 droughts.

-   @leitoldNinoDroughtIncreased2018 increased canopy turnover during drought.
    Similar increase in continuous and (large) fragments.
    Increase in turnover more variable in fragments.
    Coarse woody debris increased 62% during drought.\

@@

-   Ecological Consequences of these patterns: an eye towards a drier/wetter future
